---
title: "Quarto for Reproducible Research"
---

```{r setup-engines, include=FALSE}
# Register missing engines for clean rendering
knitr::knit_engines$set(markdown = function(options) {
  knitr::engine_output(options, options$code, "")
})
knitr::knit_engines$set(shell = function(options) {
  knitr::engine_output(options, options$code, "")
})
```

# NDMC/EPHI Training Materials

**Live site**: [https://mesfind.github.io/qmd/](https://mesfind.github.io/qmd/)

## 🔄 **Reproduce Locally (2 minutes)**

```{r}
#| label: use-course
#| echo: true
#| eval: false
# Download complete training materials
usethis::use_course("mesfin/qmd")
```

```{bash}
#| label: quarto-render
#| eval: false
# Navigate to folder
cd qmd

# Build book (25 files → docs/)
quarto render

# Preview locally
quarto preview docs/
```

## **Core Training (Half-Day Workshop)**

1. **[Installation](installation.qmd)** ← **START HERE** - R + Quarto setup
2. **[Why Quarto?](why-qmd.qmd)** - Reproducible research benefits
3. **[RStudio Setup](rstudio.qmd)** - Projects + workspace
4. **[Workflow](workflow.qmd)** - NDMC best practices
5. **[Basic Documents](using-qmd.qmd)** - First `.qmd` file
6. **[PDF/HTML/Word](pdf-html-word.qmd)** - Multi-format export
7. **[Keyboard Shortcuts](keyboard-shortcuts.qmd)** - 10x productivity
8. **[Figures & Tables](figures-tables-captions.qmd)** - Maps + risk tables
9. **[Custom Visuals](changing-figures.qmd)** - Resize + save plots
10. **[Mathematics](math.qmd)** - SIR models + equations

## **Reference Materials**

- **[Cross-references](cite-fig-tab-sec.qmd)** - `@fig-malaria-map`, `@tbl-risk`
- **[Citations](citations-and-styles.qmd)** - BibTeX for Gates proposals
- **[Troubleshooting](common-problems.qmd)** - Fix common errors
- **[Dashboards/Slides](alternative-outputs-and-exts.qmd)** - Surveillance reports
- **[Next Steps](next-steps.qmd)** - Earth Engine + parameterized reports

## **Appendices**

- **[Visual vs Source Mode](appendix-visual-vs-source-mode.qmd)**
- **[Course Template](appendix-template.qmd)**
- **[FAQ](appendix-faq.qmd)**
- **[HTML Extensions](appendix-html-extensions.qmd)**
- **[Manuscripts](appendix-manuscript.qmd)**

---

**Public Health Data Science Training**  
**[References](references.qmd)** | **[Acknowledgements](acknowledgements.qmd)** | **[License](license.qmd)**

---

## **Training Flow**
```
1. usethis::use_course("mesfin/qmd")    → Download
2. quarto render                        → Build docs/
3. quarto preview docs/                 → Train at localhost:8000
```


