---
title: "Quarto for Reproducible Research"
---

```{r setup-engines, include=FALSE}
# Register missing engines for clean rendering
knitr::knit_engines$set(markdown = function(options) {
  knitr::engine_output(options, options$code, "")
})
knitr::knit_engines$set(shell = function(options) {
  knitr::engine_output(options, options$code, "")
})
```


# Training Material

**Live at**: [https://mesfind.github.io/qmd/](https://mesfind.github.io/qmd/)

## Core Training (Half-Day Workshop)

- **[Why Quarto?](installation.qmd)** - Reproducible research for public health
- **[Installation](why-qmd.qmd)** ← **Start here** - RStudio + TinyTeX setup  
- **[RStudio Setup](rstudio.qmd)** - Projects and workspace management
- **[Workflow](workflow.qmd)** - Best practices for NDMC teams
- **[Basic Documents](using-qmd.qmd)** - First Quarto file
- **[PDF/HTML/Word](pdf-html-word.qmd)** - Multi-format export
- **[Keyboard Shortcuts](keyboard-shortcuts.qmd)** - Speed up coding
- **[Figures & Tables](figures-tables-captions.qmd)** - Disease maps + risk tables
- **[Custom Visuals](changing-figures.qmd)** - Resize, save, format plots
- **[Mathematics](math.qmd)** - SIR models and equations

## Reference & Advanced

- **[Cross-references](cite-fig-tab-sec.qmd)** - `@fig-map`, `@tbl-risk`
- **[Citations](citations-and-styles.qmd)** - BibTeX for proposals
- **[Equations](caption-reference-eqn.qmd)** - Numbered formulas
- **[Troubleshooting](common-problems.qmd)** - Fix common errors
- **[Dashboards/Slides](alternative-outputs-and-exts.qmd)** - Surveillance + presentations
- **[Next Steps](next-steps.qmd)** - Parameterized reports, Earth Engine

## Appendices

- **[Visual vs Source Mode](appendix-visual-vs-source-mode.qmd)**
- **[Course Template](appendix-template.qmd)**
- **[FAQ](appendix-faq.qmd)**
- **[HTML Extensions](appendix-html-extensions.qmd)**
- **[Manuscripts](appendix-manuscript.qmd)**

## Download for Training

```{r}
#| label: use-course
#| echo: true
#| eval: false
usethis::use_course("mesfin/qmd")
