```markdown
# Installation

```{r setup-engines, include=FALSE}
# Register missing engines for clean rendering
knitr::knit_engines$set(markdown = function(options) {
  knitr::engine_output(options, options$code, "")
})
knitr::knit_engines$set(shell = function(options) {
  knitr::engine_output(options, options$code, "")
})
```

**NDMC/EPHI Training Setup** - Get everyone ready for Quarto in 15 minutes.

## Overview

* **Duration**: 15 minutes
* **Goal**: Install R, RStudio, Quarto + test public health workflows

## Software Stack

### R (Version 4.4+)

::: {.panel-tabset}

#### Windows
[Download R](https://cloud.r-project.org/bin/windows/)

#### macOS  
[Download R](https://cloud.r-project.org/bin/macosx/)

#### Linux (Ubuntu/Debian)
```bash
sudo apt update
sudo apt install r-base
```

:::

### RStudio Desktop (2024+)

[Download RStudio](https://posit.co/download/rstudio-desktop/#download)

### Quarto (v1.5+)

[Quarto Install](https://quarto.org/docs/get-started/)

**One command installs everything**:
```bash
quarto install tinytex  # Includes lightweight LaTeX
```

## Verify Installation

```{r}
#| label: install-packages
#| eval: false
# Core packages for NDMC workflows
install.packages(c(
  "quarto", "knitr", "rmarkdown",
  "tidyverse", "here", "broom", 
  "fs", "usethis", "gapminder"
))
```

## PDF Engine (LaTeX)

**Quarto includes TinyTeX** (<200MB) - no separate LaTeX install needed!

```{r}
#| label: tinytex-check
#| eval: false
# Run once per machine
tinytex::install_tinytex()
```

**Terminal alternative**:
```bash
quarto install tinytex
```

## Test NDMC Workflow

```{r}
#| label: ndmc-test
#| eval: false
# Verify everything works
library(tidyverse)
library(here)
library(quarto)

# Test file creation
file.create(here("test.qmd"))
```

## Troubleshooting

| Issue | Solution |
|-------|----------|
| `Rscript not found` | Restart RStudio |
| `tinytex_root() error` | `tinytex::reinstall_tinytex()` |
| `quarto not found` | Add to PATH: `export PATH=$PATH:/Applications/Quarto/bin` |

**Success**: All libraries load → Ready for training!

---
**[Next: Why Quarto?](why-qmd.qmd)**

**Live training**: https://mesfind.github.io/qmd/installation.html
```